Test functions on Alabama data

### 2016-09-28 Code/Test life expectancy fxs on Alabama.Rmd

```{r exploratory graphs}
ggplot(cod.tab.alabama.male.1969, aes(x=COD2, y=prop1)) + 
  geom_point(aes(col="White")) + geom_point(aes(y=prop2, col="Black")) +
  scale_y_continuous(name = "Proportion dying from specified cause") +
  facet_wrap(~Age2) + theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

```{r}
life.table.whites <- data.frame(life.table(data = first.strata, num.ages.in.group = "nx", death.counts = "total_deaths5", population.counts = "Population"))

life.table.blacks <- data.frame(life.table(data = second.strata, num.ages.in.group = "nx", death.counts = "total_deaths5", population.counts = "Population"))

alabama_age_decomp <- le_age_decomp(life.table1 = life.table.blacks, name.lt1 = "Blacks", 
                                    life.table2 = life.table.whites, name.lt2 = "Whites", age.groups = "Age3")
alabama_age_decomp

ggplot(alabama_age_decomp, aes(y = C_x, x = Ages)) + geom_point() + scale_y_continuous("Contribution of Age to Gap")
sum(alabama_age_decomp$C_x)
life.table.whites$e_x[1] - life.table.blacks$e_x[1]

ggplot(alabama_age_decomp, aes(y = Life_Expectancy_1, x = Ages)) + geom_point(aes(col="Black")) + scale_y_continuous("Life Expectancy (Yrs)") +
  geom_point(aes(y = Life_Expectancy_2, col="White"))

alabama_cod_decomp <- cause_of_death_decomp(life.table1 = life.table.blacks, life.table2 = life.table.whites, decomp.table = alabama_age_decomp,
                      cod.table = cod.tab.alabama.male.1969, "Age2", "COD2", "prop1", "prop2")
```

>>>>

```{r exploratory_graphs}
ggplot(cod.tab.alabama.male.1969, aes(x=COD2, y=prop1)) + 
  geom_point(aes(col="White")) + geom_point(aes(y=prop2, col="Black")) +
  scale_y_continuous(name = "Proportion dying from specified cause") +
  facet_wrap(~Age2) + theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

```{r life-tables}
life.table.whites <- data.frame(life.table(data = first.strata, num.ages.in.group = "nx", death.counts = "total_deaths5", population.counts = "Population"))

life.table.blacks <- data.frame(life.table(data = second.strata, num.ages.in.group = "nx", death.counts = "total_deaths5", population.counts = "Population"))
```

The life expectancy at birth for white males in Alabama in 1969 is `r life.table.whites$e_x[1]` years vs. `r life.table.blacks$e_x[1]` for black males, for a gap of `r life.table.whites$e_x[1] - life.table.blacks$e_x[1]` years.

```{r age-decomp}
alabama_age_decomp <- le_age_decomp(life.table1 = life.table.blacks, name.lt1 = "Blacks", 
                                    life.table2 = life.table.whites, name.lt2 = "Whites", age.groups = "Age3")
alabama_age_decomp

sum(alabama_age_decomp$C_x)

ggplot(alabama_age_decomp, aes(y = C_x, x = Ages)) + 
  geom_point() + 
  scale_y_continuous("Contribution of Age to Gap") +
  geom_abline(intercept = 0, slope = 0)

ggplot(alabama_age_decomp, aes(y = LE_Blacks, x = Ages)) + 
  geom_point(aes(col="Black")) + 
  scale_y_continuous("Life Expectancy (Yrs)") +
  geom_point(aes(y = LE_Whites, col="White")) +
  ggtitle("Life expectancy by age in black and white males in Alabama in 1969")
```

```{r cod-decomp}
alabama_cod_decomp <- cause_of_death_decomp(life.table1 = life.table.blacks, 
                                            life.table2 = life.table.whites, 
                                            decomp.table = alabama_age_decomp,
                                            cod.table = cod.tab.alabama.male.1969, "Age2", "COD2", "prop1", "prop2")

ggplot(alabama_cod_decomp, aes(y = C_xi, x = COD2)) + 
  geom_point() + 
  scale_y_continuous("Contribution of Age to Gap") +
  geom_abline(intercept = 0, slope = 0) +
  facet_wrap(~Age2) + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
